Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-11-14 Arxiv/main.tex
update accuracy analysis

\subsubsection{Accuracy Bound for Exponential Mechanism}
\label{subsec_accuracy_global}
The accuracy bound of exponential mechanism is given in \cite{dwork2014algorithmic} as:
\begin{equation*}
Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},
\end{equation*}
where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal candidates.

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
Given\cite{dwork2014algorithmic}:
$$
Pr[|Y| \geq t \cdot b] = e^{- t},
$$
where $Y \thicksim Lap(b)$, we get:
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}
\end{equation*}
in our case, where $Y \thicksim Lap(\frac{\Delta \bysinfer}{\epsilon})$.

After post-processing, we get:
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t \leq Y < t + 1] 
= \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
\]

@@

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}
  In Beta-binomial model,
  we have following formula for accuracy:
  \begin{align}
  \label{eq_acc}
  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c} 
  = & \frac{2 \exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\unomalizer{\dataobs}},
  \end{align}
  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$.\\
  Unfolding the Hellinegr distance in this accuracy bound:

@@

Moreover, based on the accuracy bound in Sec. \ref{subsec_accuracy_global}, we also derived a loose bound:

\begin{equation*}
\begin{split}
Pr[u(\hexpmech(\dataobs)) \leq c] 
& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
\end{split}
\end{equation*}

>>>>

% \subsubsection{Accuracy Bound for Exponential Mechanism}
% \label{subsec_accuracy_global}
% The accuracy bound of exponential mechanism is given in \cite{dwork2014algorithmic} as:
% \begin{equation*}
% Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
% 		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},
% \end{equation*}
% where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal candidates.

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
If $Y \thicksim Lap(b)$, we have\cite{dwork2014algorithmic}:
$$
Pr[|Y| \geq t \cdot b] = e^{- t}.
$$
Based on this, we get:
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}
\end{equation*}
in our case, where $Y \thicksim Lap(\frac{\Delta \bysinfer}{\epsilon})$.

After post-processing (i.e., taking the floor value of $Y$), we get:
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t \leq Y < t + 1] 
= \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
\]

@@

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}
  In Beta-binomial model,
  we have following formula for accuracy:
  \begin{align}
  \label{eq_acc}
  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c} 
  = & \frac{2 \exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
  \end{align}
  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$.\\
  Unfolding the Hellinegr distance in this accuracy formula:

@@
